---
title: "Halter_Deepak"
author: "Deepak"
date: "17/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Importing required libraries
```{r}
library(ggplot2)
library(timelineR)
library(geosphere)
library(circular)
library(lubridate)
library(dplyr)
library(ggpubr)
```



## Importing and viewing the structure of the dataset
```{r}
Mydata <- read.csv('Core Systems Analyst – Technical Assessment Dataset.csv',fileEncoding="UTF-16LE",sep = '\t',header=TRUE,stringsAsFactors = FALSE)
Mydata$NZDT <- dmy_hms(Mydata$NZDT)
head(Mydata)
str(Mydata)

```

## Creating a new column with corrected heading assuming error in IMU data
```{r}
corrected_Heading <- lapply(Mydata$Heading, function(x) ifelse(x > 360, abs(360-x) , x))

Mydata$corrected_Heading <- corrected_Heading

Mydata$corrected_Heading <- as.numeric(unlist(Mydata$corrected_Heading))

head(Mydata)


Mydata$corrected_Heading[1]


```
#### Initial approach using degrees by bringing all data into 0-180 deg quadrants(to be considered if decided to work with the same unit)
```{r}
variation <- list()
for (i in 1:length(Mydata$Heading)) {
    if (Mydata$GPS.Heading[i] > 180) {
        if (Mydata$corrected_Heading[[i]] > 180) {
            var <- abs(Mydata$GPS.Heading[i] - Mydata$corrected_Heading[[i]])
        }
        else {
            var <- (360-Mydata$GPS.Heading[i]) + Mydata$corrected_Heading[[i]]
        }     
    }  
    else {
        if (Mydata$corrected_Heading[[i]] < 180) {
            var <- abs(Mydata$GPS.Heading[i] - Mydata$corrected_Heading[[i]])
        }
        else{
            var <- Mydata$GPS.Heading[i] + (360- Mydata$corrected_Heading[[i]])
        }
    }   
    variation <- rbind(variation,var)
}
   
```

```{r}
Mydata$variation <- variation
```


```{r}
Mydata$variation <- as.numeric(unlist(variation))

mean(Mydata$variation)

hist(Mydata$variation)

head(Mydata)

write.csv(Mydata,'Mydata.csv')
```



```{r}
plot_grob <- plot_timeline(Mydata,data_cols = c('NZDT','variation','GPS.Heading','Heading','GPS.Speed'))

plot(plot_grob)
```

## Bringing the data to two quadrants and looking into variations
```{r}
var_Head <- list()
for (i in 1:length(Mydata$Heading)) {
    if(Mydata$corrected_Heading[i]>180){
        var <- (360 - Mydata$corrected_Heading[i])
    }
    else {
        var <- Mydata$corrected_Heading[i]
    }
    var_Head <- rbind(var_Head,var)
}
```


```{r}
var_Head <- as.numeric(unlist(var_Head))

```

```{r}
var_GPSHead <- list()
for (i in 1:length(Mydata$Heading)) {
    if(Mydata$GPS.Heading[i]>180){
        var <- (360 - Mydata$GPS.Heading[i])
    }
    else {
        var <- Mydata$GPS.Heading[i]
    }
    var_GPSHead <- rbind(var_GPSHead,var)
}
```

```{r}
var_GPSHead <- as.numeric(unlist(var_GPSHead))
```
##### May  not be actual mean for circular data. To look into actual mean refer to the section working with radians
```{r}
mean(Mydata$GPS.Speed)
```


```{r}
Mydata$var_Head <- var_Head
Mydata$var_GPSHead <- var_GPSHead
```


```{r}
ggplot(Mydata, aes(x=var_GPSHead, y=var_Head, group=Serial.Number, color=Serial.Number)) + 
geom_point()
```


## Approaching the data working with radians using circulate package
```{r}
anglecir =  conversion.circular(Mydata$Heading, type="angles", units="rad",modulo="2pi", template='geographics')
summary(anglecir)
```

## Readings are converted to radians and the corresponding column is added
```{r}
var_Head_rad <- list()
for (i in 1:length(Mydata$Heading)) {
    var <- rad(Mydata$corrected_Heading[i])
    var_Head_rad <- rbind(var_Head_rad,var)
}
Mydata$var_Head_rad <- as.numeric(unlist(var_Head_rad))
```


```{r}
var_GPSHead_rad <- list()
for (i in 1:length(Mydata$Heading)) {
    var <- rad(Mydata$GPS.Heading[i])
    var_GPSHead_rad <- rbind(var_GPSHead_rad,var)
}
Mydata$var_GPSHead_rad <- as.numeric(unlist(var_GPSHead_rad))
```


```{r}
head(Mydata)
```

## Calculating summary statistics using circular package
```{r}
mean_head <- mean.circular(Mydata$var_Head_rad)
mean_head_gps <- mean.circular(Mydata$var_GPSHead_rad)
mean_head
mean_head_gps
```


```{r}
sd_head <- sd.circular(Mydata$var_Head_rad)
sd_head_gps <- sd.circular(Mydata$var_GPSHead_rad)
```

## Establishing Confidence Intervals
```{r}
max_interval_head <- mean_head + (2*sd_head)
min_interval_head <- mean_head - (2*sd_head)
```

```{r}
min_interval1 <- rad(360) + min_interval_head
max_interval1 <- rad(360)
min_interval2 <- rad(0)
max_interval2 <- max_interval_head
```


## Assigning class 1 and class 0 for hypothesis test
```{r}
class <- list()
for (i in 1:length(Mydata$GPS.Heading)) {
    val1 <- Mydata$var_GPSHead_rad[i]
    val2 <- Mydata$var_Head_rad[i]
    if((((val1 <= max_interval1) & (val1 >= min_interval1)) | ((val1 <= max_interval2 ) & (val1 >= min_interval2))) & (((val2 <= max_interval1) & (val2 >= min_interval1)) | ((val2 <= max_interval2 ) & (val2 >= min_interval2)))) {
        var <- 1
    }  
    else {
        var <- 0
    }
        class <- rbind(class, var)
}
   
```


```{r}
Mydata$class <- as.numeric(unlist(class))
```

```{r}
head(Mydata)

```


# Finding the total number of cows falling under class 1 and class 0
```{r}
cow_class <- table(Mydata$class)
cow_class
plot(cow_class,xlab = "Class",ylab = "Total sample size")

```


## Proportion Z test for hypothesis testing
```{r}
prTest <- prop.test(3215,3309, p=0.95,correct = FALSE)
prTest
```
### At 95% confidence the null hypothesis cant be rejected.
